\vspace{-2em}The 4th Workshop on Sustainable Software for Science: Best Practices and Experiences (WSSSPE4)

### 2016-06-12 WSSSPE4_proposal/WSSSPE4_proposal.tex
edit in Allen prior support

\textbf{Daniel S.~Katz}
was most recently supported by the NSF as a Program Officer under NSF ACI-1239751, made to the University of Chicago for \$999,966 for the period 3/26/2012 to 3/25/2016.  {\bf Intellectual Merit:} A large number of publications were produced under the PI's IRD time in this award, including the WSSSPE1 and WSSSPE2 reports~\cite{WSSSPE1, WSSSPE2}. These documents and this work have impacted our understanding of the issues related to sustainable scientific software.  {\bf Broader Impacts:}
A number of NSF programs (e.g., SI2, CDS\&E) and official documents were produced under this award (e.g., \cite{NSF_software_vision}).  These programs have added and developed an emphasis on software as infrastructure at NSF, and the software produced under these programs have impacted both education and industry.

\textbf{Gabrielle D.~Allen}
was the PI for two recent workshop awards related to sustainable software. NSF CCF-1551592, made to the University of Illinois for \$88,739 for the period 09/15/2015 to 5/31/2017 supported the workshop on Computational Science \& Engineering Software Sustainability and Productivity Challenges (CSSSPE) which was hosted by NITRD and supported by NSF, DOE and DOD and brought together a very diverse number of agency representatives, software developers and software engineers spanning academia, national labs and industry. A report from this workshop is imminent. 
Allen was also PI for a previous award supporting WSSSPE2 and WSSSPE3, NSF ACI-1434218, made to the University of Illinois for \$24,758 for the period 5/1/2014 to 4/30/2016.  {\bf Intellectual Merit:} Publications  resulting from the WSSSPE2 and WSSSPE3 workshop include \cite{WSSSPE2-collection, WSSSPE2, WSSSPE3}. {\bf Broader Impacts:} The award funded participation at WSSSPE2 and WSSSPE3 by early career researchers and underrepresented groups.

>>>>

\textbf{Daniel S.~Katz}
was most recently supported by the NSF as a Program Officer under NSF ACI-1239751, made to the University of Chicago for \$999,966 for the period 3/26/2012 to 3/25/2016.  {\bf Intellectual Merit:} A large number of publications were produced under the PI's IRD time in this award, including the WSSSPE1-WSSSPE3 reports~\cite{WSSSPE1, WSSSPE2, WSSSPE3}. These documents and this work have impacted our understanding of the issues related to sustainable scientific software.  {\bf Broader Impacts:}
A number of NSF programs (e.g., SI2, CDS\&E) and official documents were produced under this award (e.g., \cite{NSF_software_vision}).  These programs have added and developed an emphasis on software as infrastructure at NSF, and the software produced under these programs have impacted both education and industry.

\textbf{Gabrielle D.~Allen}
was the PI for two recent workshop awards related to sustainable software. NSF CCF-1551592, made to the University of Illinois for \$88,739 for the period 09/15/2015 to 5/31/2017 supported the workshop on Computational Science \& Engineering Software Sustainability and Productivity Challenges (CSSSPE) which was hosted by NITRD and supported by NSF, DOE and DOD and brought together a very diverse number of agency representatives, software developers and software engineers spanning academia, national labs and industry. A report from this workshop is imminent. 
Allen was also PI for a previous award supporting WSSSPE2 and WSSSPE3, NSF ACI-1434218, made to the University of Illinois for \$24,758 for the period 5/1/2014 to 4/30/2016.  {\bf Intellectual Merit:} The workshops helped us gain knowledge about sustainable software and in particular, sustainable software in science, includes examining the roles of formal software engineering, metics, economics, workforce development, and sociology in scientific software development.
Publications  resulting from the WSSSPE2 and WSSSPE3 workshop include \cite{WSSSPE2-collection, WSSSPE2, WSSSPE3}. {\bf Broader Impacts:} The awards funded participation at CSESSP and WSSSPE2 \& WSSSPE3 by early career researchers and underrepresented groups, diversifying the pool of researchers interested and active in working towards sustainable software.
